---
title: "Working with Web APIs"
author: "A H M Shahparan"
date: "3/31/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The New York Times web site provides a rich set of APIs, as described here: http://developer.nytimes.com/docs You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe.

####Loading libraries
```{r}
#To parse JSON data into dataframe
require (jsonlite)
#To display R data objects as tables on HTML pages
library(DT)
```

####URI Structure
We are using articlesearch API from New York Times to retrieve articles by our search terms. We need to populate a URI structure containg the web url and the API Key acquired from New York Times by simply using the `paste()` command.

```{r}
baseUrl <- "https://api.nytimes.com/svc/search/v2/articlesearch.json"
apiKey <- "?api-key=1b5b89d9860f42cba5d3db52032f1ef8"
uri <- paste(baseUrl, apiKey, sep="") 
uri
```

####Adding up a query
Search query term. Search is performed on the article body, headline and byline etc. Like the API key, we paste the query into the URl. We will use `URLencode` function to percent-encode characters in URL (). 
```{r}
query <- "&q=Data Science"
uri <- paste(uri, URLencode(query), sep="")
uri
```

####Convert to R dataframe
Now we will use fromJSON function to parse JSON data into the R data frame. Once we have it parsed, we choose to get the docs porition of the response data as we get our desired data there.

```{r}
jsonContent <- fromJSON(uri)
df <- jsonContent$response$docs
colnames(df)
```

We use `flatten` function that automatically flattens nested data frames into a single non-nested data frame.
```{r}
flatdf <- flatten(df)
colnames(flatdf)
```

Subsetting the falt data based on columns of interest and then displaying the data as a table on HTML page. 
```{r}
subsetData <- flatdf[ , c("pub_date", "web_url","headline.main", "byline.original", "snippet")]
options(DT.options = list(pageLength = 5))
datatable(subsetData)
```


